
\documentclass{article} % For LaTeX2e
\usepackage{iclr2024_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx} 
\usepackage[most]{tcolorbox}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{array}
\usepackage[usestackEOL]{stackengine}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{subcaption}


\newcommand{\hide}[1]{}

\newtcolorbox{promptbox}[1][]{
  breakable,
  title=#1,
  colback=gray!5,
  colframe=black,
  colbacktitle=gray!15,
  coltitle=black,
  fonttitle=\bfseries,
  bottomrule=1.5pt,
  toprule=1.5pt,
  leftrule=1pt,
  rightrule=1pt,
  arc=0pt,
  outer arc=0pt,
  enhanced,
  before upper={\parindent=1.5em} % This sets the paragraph indentation
}

\lstset{
  basicstyle=\ttfamily,
  breaklines=true,
  breakatwhitespace=false,
  columns=flexible,
  keepspaces=true,
  showspaces=false,
  showstringspaces=false,
  showtabs=false,
  tabsize=4,
  xleftmargin=0pt,
  xrightmargin=0pt
}

\newcommand{\aspace}{\hspace{1em}}

\title{CogVideoX: A Text-to-Video Diffusion Model with Expert Transformer}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.


\author{Zhuoyi Yang\aspace Jiayan Teng \aspace Wendi Zheng\aspace Ming Ding\aspace Shiyu Huang \aspace Jiazheng Xu \aspace \\
\textbf{Yuanming Yang \aspace Xiaohan Zhang \aspace Xiaotao Gu 
\aspace Guanyu Feng \aspace  Da Yin \aspace Wenyi Hong \aspace } \\
\textbf{ Weihan Wang \aspace Yean Cheng \aspace Yuxuan Zhang \aspace Ting Liu \aspace Bin Xu \aspace Yuxiao Dong \aspace Jie Tang} \\
$^1$Zhipu AI\ \ \ \ \ \ $^2$Tsinghua University \\
\href{https://github.com/THUDM/CogVideo}{https://github.com/THUDM/CogVideo}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\renewcommand{\thefootnote}{}
\footnotetext{Zhuoyi and Jiayan made equal contributions. Core contributors: Zhuoyi, Jiayan, Wendi, Ming, and Shiyu.}
\footnotetext{{\{yangzy22,tengjy20\}@mails.tsinghua.edu.cn, \{yuxiaod,jietang\}@tsinghua.edu.cn}}
%\footnotetext{$^\dagger$ corresponding authors}
\renewcommand{\thefootnote}{\arabic{footnote}}
\begin{abstract}
We introduce CogVideoX, a large diffusion transformer model capable of generating videos conditioned on text prompts. It applies a 3D VAE and a 3D transformer based on Expert Adaptive LayerNorm. Employing a progressive training technique, the model is able to generate coherent long-duration videos characterized by significant motion. Additionally, we propose a complete large-scale data processing pipeline, including various data cleaning strategies and video re-caption method, resulting in better generation quality and improved semantic alignment. Finally, CogVideoX achieves state-of-the-art performance across multiple machine metrics and human evaluations.
\end{abstract}

\input{sections/introduction}
\input{sections/vae}
\input{sections/model}
\input{sections/data}
\input{sections/pretraining}
\input{sections/abaltion}
\input{sections/results}




% \subsubsection*{Author Contributions}

% \textbf{Model Training}: Zhuoyi Yang, Jiayan, Teng

% \textbf{VAE Training}: Wendi Zheng

% \textbf{Data Process}: Jiyan Teng, Zhuoyi Yang, Ting Liu, Zhiming Zhang, Jieming Zhong

% \textbf{Video Caption}: Shiyu Huang

% % \textbf{Data Collection}: Zhao Xue, Baoxu Wang

% \textbf{Data Annotation Organization}: Zhengjia Xu, Xiaohan Zhang

% \textbf{Evaluation}: Yuanming Yang, Xiaotao Gu Team, Mingxiang Liao

% \textbf{Technical Advisor}: Ming Ding

% % \textbf{Inference Optimization}: Guanyu Feng, Da Yin, Jingsen Wang

% \textbf{Cluster Operation Support}: Aohan Zeng Team


\subsubsection*{Acknowledgments}
This research was supported by Zhipu AI. Thanks to BiliBili for data support. Thanks to all our collaborators and partners from Knowledge Engineering Group (KEG) and Zhipu AI.


\bibliography{reference}
\bibliographystyle{iclr2024_conference}

\clearpage
\appendix
\input{appendix/image2video}
\input{appendix/caption_upsampler}
\input{appendix/video_caption_gen}
\input{appendix/video_caption_example}
\input{appendix/video2video}
\input{appendix/human_evaluation}

\end{document}
